---
title: ''
output:
  html_document:
    code_folding: hide
    theme: readable
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
date: '`r Sys.Date()`'
params:
  Owner: Sean Lopp
  pwd: stop("Need password")
---


```{r knitr_init, echo=FALSE, cache=FALSE, message=FALSE}
library(knitr)
library(rmdformats)

## Global options
options(max.print="75", scipen = 10)
opts_chunk$set(echo=TRUE,
               cache=FALSE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE,
               scipen=0)
opts_knit$set(width=75)

library(RForcecom)
library(dplyr)
library(lubridate)
library(DT)
library(dygraphs)
library(ggplot2)
library(xts)
library(forecast)
```


```{r Get SalesForce Connection, message=FALSE, include=FALSE}

#source("promptSFCredentials.R")
#sf <- promptSFCredentials() 
#if(!exists("sf")) stop("Need Salesforce context named 'sf'")
sf<-rforcecom.login("sean@rstudio.com",
                    paste(params$pwd,"FXnvB1VTBeUNDK4b02C2KlZR9"
,sep=""),
"na9.salesforce.com", "26.0")
```

# `r params$Owner`  Sales Report
```{r GetData}
q <- "Select Opportunity.Owner.Name, Type, Amount, CloseDate, Account.Name, IsWon, IsClosed FROM Opportunity"
d <- rforcecom.query(sf, q)
```

## Open Deals {.tabset}

### This Month

```{r}
d.sub <- d %>% mutate(CloseDate=ymd(CloseDate)) %>% 
  filter(Owner.Name==params$Owner, IsWon=="false",IsClosed=="false", 
         month(CloseDate)==month(today()), 
         year(CloseDate)==year(today())) %>% 
  select(Amount, Account.Name, Type)
```

This month I have a total of `r nrow(d.sub)` deals remaining open for a total of $`r sum(d.sub$Amount)`.

```{r}
ggplot(aes(x=Type,y=Amount, fill=Type), data=d.sub) + 
  geom_bar(stat="identity")
DT::datatable(d.sub,options = list()) %>% formatCurrency("Amount")
```

### This Quarter

```{r OCurrentQuarter}

d.sub <- d %>% mutate(CloseDate=ymd(CloseDate), 
                      CloseMonth=month(CloseDate)) %>%
  filter(Owner.Name==params$Owner, IsWon=="false", IsClosed=="false",
         lubridate::quarter(CloseDate)==lubridate::quarter(today()),
         year(CloseDate)==year(today())) %>% 
  select(Amount, Account.Name, Type,CloseMonth)

```

This quarter I have a total of `r nrow(d.sub)` deals remaining open for a total of $`r sum(d.sub$Amount)`.

```{r OQResults}
d.sub <- d.sub %>% arrange(Type)
ggplot(aes(x=CloseMonth,y=Amount, fill=Type), data=d.sub) + 
  geom_bar(stat="identity")

DT::datatable(d.sub,options = list())%>% formatCurrency("Amount")
```



### Next Quarter

```{r NextQuarter}

d.sub <- d %>% mutate(CloseDate=ymd(CloseDate),
                      CloseMonth=month(CloseDate)) %>%
  filter(Owner.Name==params$Owner, IsWon=="false", IsClosed=="false",
         lubridate::quarter(CloseDate)==(lubridate::quarter(today())+1),
         year(CloseDate)==year(today())) %>% 
  select(Amount, Account.Name, Type,CloseDate,CloseMonth)

```

This quarter I have a total of `r nrow(d.sub)` deals remaning open for a total of $`r sum(d.sub$Amount)`.

```{r NQResults}
d.sub <- d.sub %>% arrange(Type)
ggplot(aes(x=CloseMonth,y=Amount, fill=Type), data=d.sub) + 
  geom_bar(stat="identity")

d.sub <- d.sub %>% arrange(CloseDate)

DT::datatable(d.sub) %>% formatCurrency("Amount")
```


## Closed Deals {.tabset}

### This Month



```{r Monthly}
d.sub <- d %>% mutate(CloseDate=ymd(CloseDate)) %>% 
  filter(Owner.Name==params$Owner, IsWon=="true",
         month(CloseDate)==month(today()),
         year(CloseDate)==year(today())) %>% 
  select(Amount, Account.Name, Type)
```

So far this month I have closed a total of `r nrow(d.sub)` deals for a total of $`r sum(d.sub$Amount)`.

```{r Results}
ggplot(aes(x=Type,y=Amount, fill=Type), data=d.sub) + 
  geom_bar(stat="identity")
DT::datatable(d.sub,options = list())%>% formatCurrency("Amount")
```

### This Quarter

```{r CurrentQuarter}

d.sub <- d %>% mutate(CloseDate=ymd(CloseDate),
                      CloseMonth=month(CloseDate))%>%
  filter(Owner.Name==params$Owner, IsWon=="true",
         lubridate::quarter(CloseDate)==lubridate::quarter(today()),
         year(CloseDate)==year(today())) %>%
  select(Amount, Account.Name, Type,CloseMonth)

```

So far this quarter I have closed a total of `r nrow(d.sub)` deals for a total of $`r sum(d.sub$Amount)`.

```{r QResults}
d.sub <- d.sub %>% arrange(Type)
ggplot(aes(x=CloseMonth,y=Amount, fill=Type), data=d.sub) + 
  geom_bar(stat="identity")

DT::datatable(d.sub,options = list())%>% formatCurrency("Amount")
```

## Closed / Target / Forecast {.tabset}

```{r TotalForecast}
#calculate target by assuming proportions will remain constant
sales <- d %>% mutate(CloseDate=ymd(CloseDate)) %>%
  filter(year(CloseDate)>2014, year(CloseDate)<year(today())) %>%
  group_by(month(CloseDate)) %>% 
  summarise(total=sum(Amount, na.rm=TRUE))

p <- sales$total/sum(sales$total)
target <- rep(32500000/12,12)*p

#closed deals
d.sub<- d %>% mutate(CloseDate=ymd(CloseDate)) %>%
  filter(Owner.Name==params$Owner, IsWon=="true",
         year(CloseDate)==year(today()),
         month(CloseDate)<month(today())|
           month(CloseDate)==month(today())) %>% 
  group_by(month=month(CloseDate)) %>% 
  summarize(total=sum(Amount,na.rm=TRUE)) %>% 
  arrange(month) %>% 
  select(total)

closed <- c(d.sub$total, rep(NA,12-length(d.sub$total)))


# get forecasted deals
d.sub<- d %>% mutate(CloseDate=ymd(CloseDate)) %>%
  filter(Owner.Name==params$Owner, IsWon=="false",IsClosed=="false",
         month(CloseDate)>month(today()), 
         year(CloseDate)==year(today())) %>% 
  group_by(month=month(CloseDate)) %>% 
  summarize(total=sum(Amount,na.rm=TRUE)) %>% 
  arrange(month) %>% 
  select(month,total)

forecasts <- data.frame(month=seq(1:12),total=rep(NA,12))
forecasts <- forecasts[-d.sub$month,]
forecasted <- rbind(forecasts,d.sub) %>% arrange(month) %>% 
  select(total) %>% 
  as.matrix()


#assemble and plot the data

dates <-seq(mdy('1-1-2016'),mdy('12-31-2016'), by='month')
x <- data.frame("Target"=target,"Closed"=closed,"Forecasted"=forecasted)
D <- xts(x,order.by=dates)

dygraph(D, main="Sales Data")
```



The 'target' category assumes the monthly proportion will be constant year over year and is based on a sales target of 3.25 million (expansion and renewals)

## Company Sales Projection

```{r CompanyARIMA}

# add a seasonally adjusted arima forecaset to closed deals
hist <- d %>% mutate(CloseDate=ymd(CloseDate)) %>%
  filter(year(CloseDate)>2013, CloseDate < ymd(floor_date(today(),"month")),
         IsWon=="true",IsClosed=="true") %>%
  group_by(m=month(CloseDate), y=year(CloseDate)) %>%
  summarise(total=sum(Amount, na.rm=TRUE)) %>%
  mutate(date=mdy(paste(m,"1",y,sep="-")))

hist <- xts(hist$total, order.by = hist$date)
h <- as.matrix(hist)
fit <- Arima(hist, order=c(1,1,1), seasonal=list(order=c(1,1,1),period=4))
fits <- as.matrix(fitted(fit))
f.length <- 12 - month(today())+1

f <- forecast(fit,h=f.length)

model <- c(fits,f$mean)
hist <- c(h,rep(NA,f.length))
h.length <- length(hist)-f.length 
low <- c(rep(NA,h.length),f$lower[,"95%"])
upper<- c(rep(NA,h.length),f$upper[,"95%"])

x <- data.frame(Historical=hist,Model=model,Lower.95=low, Upper.95=upper)
dates <- seq(ymd("2014-01-01"),ymd(ceiling_date(today(),"year")-months(1)),by='months')

D <- xts(x,order.by=dates)
dygraph(D, main="Total Sales: Historical and Forecast") %>% 
  dySeries("Historical", color="blue") %>% 
  dySeries(c("Lower.95","Model","Upper.95"), color="green")

# annual cummulative sales
D.cum <- D %>% as.data.frame() %>% 
  mutate(Date=ymd(rownames(.))) %>% 
  filter(year(Date)==year(today())) %>% 
  select(Historical, Model,Date)
D.cum[is.na(D.cum)] <- 0
D.cum$Historical <- cumsum(D.cum$Historical)/1000000
D.cum$Historical[(12-f.length+1):12]<-NA
D.cum$Model <-cumsum(D.cum$Model)/1000000

D.cum <- xts(x=D.cum[,c("Historical","Model")],order.by=D.cum$Date)

dygraph(D.cum, main="Annual Cummulative Sales ($mils)") %>% 
  dySeries("Historical", color="blue",stepPlot=TRUE, fillGraph=TRUE) %>% 
  dySeries("Model", color="green",stepPlot=TRUE, fillGraph=TRUE)
  

```

'Model' refers to a seasonally adjusted ARIMA model. The seasonal adjustment is done by quarter, the model paramteres are 1,1,2.



## Churn {.tabset}

### Month

Renewals Lost this Month
```{r}
d.sub <- d %>% mutate(CloseDate=ymd(CloseDate)) %>% 
  filter(Owner.Name==params$Owner, IsWon=="false",IsClosed=="true",
         month(CloseDate)==month(today()),
         year(CloseDate)==year(today()),
         Type=="Renewal") %>% 
  select(Amount, Account.Name)

DT::datatable(d.sub)%>% formatCurrency("Amount")
```

### Year

```{r}
d.sub <- d %>% mutate(CloseDate=ymd(CloseDate)) %>% 
  filter(Owner.Name==params$Owner, IsWon=="false",IsClosed=="true",
         year(CloseDate)==year(today()),
         Type=="Renewal") %>%
  mutate(month=month(CloseDate))

d.month <- d.sub %>% group_by(month) %>% 
  summarise(total=sum(Amount,na.rm=TRUE)) %>% 
  arrange(month) %>% 
  select(month,total)

if(nrow(d.month)>0){
d.months <-data.frame(month=seq(1:max(d.month$month)),
                      total=rep(0,max(d.month$month)))
d.months <- d.months[-d.month$month,]

d.months <- rbind(d.month,d.months) %>% 
  arrange(month)

ggplot(data=d.months, aes(x=month,y=total))+geom_bar(stat="identity")
}else{
  print("No Churn")
}
```

The total churn this year is `r sum(d.sub$Amount)`

```{R}
d.report <- d.sub %>% 
  select(Account.Name,Amount,month) %>% 
  arrange(desc(Amount))

DT::datatable(d.report)%>% formatCurrency("Amount")
```